---
title: "Lab 00 - Hello IDS!"
author: "Yuhang Liu"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Peter Rabbit", "Jack", "Tom", 
           "Lucica"),
  github_username = c("mcgregors-garden", "JJ", "TT", 
                      "LL"), 
  colour = c("powderblue", "azure", "bisque", 
             "brown"),
  hobby = c("Hopping", "swimming", "running", 
            "sleeping"),
  favourite_number = c(2, 3, 5, 7)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```

"This bar plot visualises the team members' favourite numbers, where each bar represents a user (by their GitHub username) with its height corresponding to their chosen number and its colour matching their preferred colour."

